\begingroup
\absone
{PERSONALIZED RESUME-JOB MATCHING SYSTEM}
{August 2014}
{Shiqiang Guo}
{B.S., Dalian Maritime University}  % Degrees ALREADY RECEIVED,
                       % e.g. {B.S., Rice University;\\
                       % M.S., Texas A\&M University}
                       % If only one degree, delete `;\\'
{Dr. Tracy Hammond}%put your advisor name here
{
Today online recruiting web sites like Monster, Indeed etc. have become one of the main channels for people to find jobs. These web platforms have provided their services for more than ten years, that saved a lot of time and cost for both job seekers and organizations who want to hire people. But users have also suffered  from  the inappropriateness  of  traditional  information  retrieval  technique. Since the result number returned to a job seeker is huge, a significant amount of reading and selection efforts are required by the job seekers. Technology to resolve this difficulty on [part of the user, recommender system technology has been studied for long time.  The  proposal will  present  a  personalize resume-job matching system, which could obtain the models from the job descriptions and resumes, and use ontology technic to find appreciate jobs for job seekers.
}
\endgroup



%\abstwo
%{First Line of Title\\Second Line of Title}
%{Month Year}
%{Your Full Name}
%{Degree, University;\\Degree, University}
%{Co-Chair's Name}
%{Co-Chair's Name}
%{Place your abstract between these braces. The text of your abstract must not
%exceed 350 words. Place your abstract between these braces. The text of your
%abstract must not exceed 350 words.}
