\begingroup
\absone
{PERSONALIZED RESUME-JOB MATCHING SYSTEM}
{August 2014}
{Shiqiang Guo}
{B.S., Dalian Maritime University}  % Degrees ALREADY RECEIVED,
                       % e.g. {B.S., Rice University;\\
                       % M.S., Texas A\&M University}
                       % If only one degree, delete `;\\'
{Dr. Tracy Hammond}%put your advisor name here
{
Today, online recruiting web sites such as Monster and Indeed have become one of the main channels for people to find jobs. These web platforms have provided their services for more than ten years, and have saved a lot of time and cost for both job seekers and organizations who want to hire people. However, traditional information retrieval techniques may not be appropriate for users. The reason is because the number of results returned to a job seeker may be huge, so job seekers are required to spend a significant amount of time reading and reviewing their options. One popular approach to resolve this difficulty for users are recommender systems, which is a technology that has been studied for a long time. 

In this thesis we have made an effort to propose a personalized job-resume matching system, which could help job seekers to find appropriate IT jobs more easily.  We create a finite state transducer based information extraction library to extract models from resumes and job descriptions. We devised a new Statistical-based ontology similarity measure to compare the resume models and the job models. Since the most appreciate jobs will be returned in front of other jobs, the users of the system could get better result than current job finding website. To evaluate the system, we had compared NDCG of the job searching results of the system to other classic information retrieval approaches, and the result showed that the system has obvious advantage than those approaches.

}
\endgroup



%\abstwo
%{First Line of Title\\Second Line of Title}
%{Month Year}
%{Your Full Name}
%{Degree, University;\\Degree, University}
%{Co-Chair's Name}
%{Co-Chair's Name}
%{Place your abstract between these braces. The text of your abstract must not
%exceed 350 words. Place your abstract between these braces. The text of your
%abstract must not exceed 350 words.}
