\chapter{CONCLUSION AND FUTURE WORK}

\section{Conclusion}
In this thesis£¬ we described JobFinder, a personalized job-resume matching system, which can help job seekers to find appropriate jobs more easily. The key technical components of the system are information extraction and ontology matching module.

In the system, job descriptions and resumes will be processed by pipeline; and a finite state transducer tool will be used to extract the models from them. The models include fields like degree, major and skills. To find the appropriate jobs, similarities between resume model and job description models will be calculated. The result will be sorted by the ontology similarity score, which is the sum of weighted multiple similarities of fields.

We proposed a finite state transducer matching library to matching the patterns in the sentences and extraction the information. We designed the a semi-automated algorithm to construct the domain specific ontology for skill set. To get the similarity between the skills, we proposed a statistical-based Ontology similarity measure.

In the experiment phrase, we evaluated the accuracy of information extraction. The ontology similarity was evaluated by NDCG. Finally, the performance of resume job matching were also tested by precision@k and NDCG,  which shows our algorithm can get better searching result than other information retrieval models.


\section{Future work}

Since finding a job is a complex process, which is affected by both subjective and objective factors.  Our work is just a initial work to solving this problem, there are a lot of parts could be improved.

First for the Information Extraction part, currently the method we used is pattern matching, we could try some machine learning approaches in future. In the resume modeling part, we could build more complex models, for resume model, which may consider the hiring history and project experience of of job seekers, and for job description model, the company's reputation and industry should be put into the models as well.

The system is a content based recommender system, mostly focus on compare the similarity between the resume and job description. In future work, we could introduce a hybrid-based recommender system, which could take advantage of other recommendation algorithms, like Collaborative Filtering. The future system all should consider more about the user's personal preference, like their location, their career development plan and so on.
