\chapter{PROBLEM}

The basic problem in this thesis is how to found appropriate job descriptions by user's resume. The systems will parse the job descriptions to the job models, and store them in database. When user searches the jobs by their resume in the system, the system will compare the resume to all the job models, and return the job descriptions sorted by their similarity value. 
   
The core idea of our algorithm is calculate similarity between resume model and job model.  
We give a formal definition of our problem. All of the notations will be used frequently throughout the thesis. 

We use $r$ denote the user's resume model, $R$ has some features $f_i$ like academic degree, their major, their skill set and so on. The symbol $J$ is the set of job models stored in the database, $j_i$ is the $ith$ job model. The similarity function $sim(r, j)$ gives the similarity value between resume $r$ and job $j$. The return list of search function $search(r,J)$ will calculate all the similarity value in the database, and the result of the function will be the job description list ranked their similarity value. The equation of how to calculate similarity value is given below:

$$ sim(r, j) = \sum_{i=1}^{n} simfun_i(r_i,j_i) \times w_i $$

The value of $sim(r, j)$ is summation of similarity value of different fields times their corresponding weight, which means different fields like major and skills,  may have different approaches to calculate their similarity value. We will describe the similarity functions of individual fields in later parts.      


 
